Improved Approximation Algorithms for the Maximum Carpool Matching Problme

### 2016-12-19 src/abstract.tex
going to think
abstract

The \textsc{\CARPOOL{}} problem is a star packing problem in directed graphs.
Formally, given a directed graph $G = (V, A)$,
a capacity function $ c: V \rightarrow \N $,
and a weight function $w : A \rightarrow \R $,
a feasible \emph{carpool matching} is a triple 
$(P, D, M)$, where $P$ (passengers) and $D$ (drivers) form a partition of $V$, 
and $M$ is a subset of $A \cap (P \times D)$,
under the constraints that for every vertex $d \in D$, 
$\din(d) \leq c(d)$, 
and for every vertex $p \in P$, $\dout(p) \leq 1$.
In the \textsc{\CARPOOL{}} problem we seek for a matching $(P, D, M)$ that maximizes the
total weight of $M$.

@@

we show that the problem can be formulated as
unconstarints submodular maximization problem, 
thus it has a 2-approximation algorithm.
For the unweighted variant of the problem when the maximum possible capacity, $C$, is
fixed, we give a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm
for the any $\varepsilon > 0$.

>>>>

The \textsc{\CARPOOL{}} problem is a star packing problem in directed graphs.
Formally, given a directed graph $G = (V, A)$,
a capacity function $c: V \rightarrow \N$,
and a profit function $p : A \rightarrow \R $,
a feasible \emph{carpool matching} is a subset of arcs, 
$M \subseteq A$, where
$\forall v \in V, 
\din[M](v) \cdot \dout[M](v) = 0, 
\din[M] \leq c(v),
\dout[M] \leq 1$. 
In the \textsc{\CARPOOL{}} problem we seek for a matching $M$
that maximizes the total profit of $M$.

@@

we show that the problem can be formulated as
unconstarints submodular maximization problem, 
thus it has a $\frac{1}{2}$-approximation algorithm.
For the unweighted variant of the problem when the maximum possible capacity, $C$, is
fixed, we give a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm
for the any $\varepsilon > 0$.

We also consider a variant of the \textsc{\CARPOOL{}} problem where every arc
has also an integral weight $w:A \to \N$ and the constraint $\din[M] \leq c(v)$
is replaced with the constraint $\sum_{(u,v)}w(u,v) \leq c(v)$.
We show that this variant of the problem can not be formulated as an
unconstarints submodular maximization as before.
We give, however, a ($2 + \varepsilon$)-approximation algorithm for this
variant, and argue that the local search algorithm can be generalized to this
variant of the problem when $C$ is fixed.
